Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-03 prob.tex
prob.tex \section{Proofs} Skip the annoy part and move on to the next...

\begin{thm}\label{thm:analogTheorem23RichmanBridges1999}~
\begin{itemize}
\item Let $f$ be a bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, 
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0'}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{0'},\frac{\pi}{2}}\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
and 
\item $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g\left(\ket{\psi}\right)\right|\le?$.\qed\end{thm}
\begin{proof}
Let $\ket{2'}=\sigma_{\ket{0}\times\ket{0'},\frac{\pi}{2}}\ket{0'}$.
Then 
\[
\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{0'}\right)+f\left(\ket{2'}\right)\right)\right|\le W_{r}-W_{l}
\]
so
\[
f\left(\ket{2'}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{0'}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
\]
whence $f\left(\ket{2}\right)\le m+W_{r}-W_{l}$. Let $\left(x,y,z\right)=\left(\ip{\psi}{0},\ip{\psi}{1},\ip{\psi}{2}\right)$
denote the coordinates of a point~$\ket{\psi}$ with respect to the
frame~$\left\{ \ket{i}\right\} _{i=0}^{2}$, then $Q\left(\ket{\psi}\right)=Mx^{2}+\left(W-M-m\right)y^{2}+mz^{2}$.

Let $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
So\footnote{\yutsung{Verify the details...}} 
\begin{eqnarray*}
 &  & \left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right|\\
 & = & \left|\left(f\left(\ket{\psi}\right)+f\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)-\left(Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)\right|\\
 & = & \left|g_{f,\ket{0}}-\left(Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right)\right|
\end{eqnarray*}
\end{proof}

>>>>

\begin{thm}\label{thm:analogTheorem23RichmanBridges1999}~
\begin{itemize}
\item Let $f$ be a bounded continuous approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, 
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0'}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{0'},\frac{\pi}{2}}\ket{0}$, $\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
and 
\item $\delta\left(\eta,W_{l},W_{r},\omega_{f}\right)=\min_{n\ge2\pi}2n\eta+4n\left(W_{r}-W_{l}\right)+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le?$.\qed\end{thm}
\begin{proof}
Let $\ket{2'}=\sigma_{\ket{0}\times\ket{0'},\frac{\pi}{2}}\ket{0'}$.
Then 
\[
\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{0'}\right)+f\left(\ket{2'}\right)\right)\right|\le W_{r}-W_{l}
\]
so
\[
f\left(\ket{2'}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{0'}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
\]
whence $f\left(\ket{2}\right)\le m+W_{r}-W_{l}$. Let $\left(x,y,z\right)=\left(\ip{\psi}{0},\ip{\psi}{1},\ip{\psi}{2}\right)$
denote the coordinates of a point~$\ket{\psi}$ with respect to the
frame~$\left\{ \ket{i}\right\} _{i=0}^{2}$, then $Q\left(\ket{\psi}\right)=Mx^{2}+\left(W-M-m\right)y^{2}+mz^{2}$.

Let $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
Then, \footnote{\yutsung{Verify the details. Especially the left-handed or right-handed
or the coordinate system, and the rotation matrix... >''<}} 
\begin{eqnarray*}
\sigma_{\ket{0},\frac{\pi}{2}}\left(x,y,z\right) & = & \left(x,-z,y\right)\\
\sigma_{\ket{2},\frac{\pi}{2}}\left(x,y,z\right) & = & \left(-y,x,z\right)
\end{eqnarray*}
Note that 
\begin{eqnarray*}
Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right) & = & 2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\\
Q\left(\ket{\psi}\right)+Q\left(\sigma_{\ket{2},\frac{\pi}{2}}\ket{\psi}\right) & = & 2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)
\end{eqnarray*}
which is the same as the quadratic form defined in corollary~\ref{thm:analogCorollary22RichmanBridges1999}.
Therefore, by corollary~\ref{thm:analogCorollary22RichmanBridges1999},
we should have 
\begin{eqnarray*}
\left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{0},\frac{\pi}{2}}\ket{\psi}\right)\right| & = & \left|g_{f,\ket{0}}-\left(2Mx^{2}+\left(W-M\right)\left(y^{2}+z^{2}\right)\right)\right|\le9\delta\left(0,W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\\
\left|f'\left(\ket{\psi}\right)+f'\left(\sigma_{\ket{2},\frac{\pi}{2}}\ket{\psi}\right)\right| & = & \left|g_{f,\ket{2}}-\left(2mz^{2}+\left(W-m\right)\left(x^{2}+y^{2}\right)\right)\right|\le9\delta\left(W_{r}-W_{l},W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)
\end{eqnarray*}
Follow the same procedure in the proof in \cite{RichmanBridges1999}.
We have 
\[
\left|f\left(\ket{\psi}\right)-M\left(x^{2}-z^{2}\right)-Wz^{2}\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{l},W_{r},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)
\]
 on the great circle $y=z$.
\end{proof}
